|

### 2023-01-30 paper_comparison/paper_comparison/paper_comparison.Rmd
fix another plot with the same problem

>>>>

dat_heter_a <- heter_conv_sim %>%
  filter(x_dist == "uniform") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(BP_p_value < 0.05)) %>%
  mutate(a = c("Left-triangle", "Butterfly", "Right-triangle")[a + 2]) %>%
  mutate(conv_or_not = "Conventional") %>%
  bind_rows(vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform", type == "heteroskedasticity") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(p_value < 0.05)) %>%
  mutate(a = c("Left-triangle", "Butterfly", "Right-triangle")[a + 2]) %>%
  mutate(conv_or_not = "Visual")) %>%
  mutate(a = factor(a, levels = c("Left-triangle", "Butterfly", "Right-triangle"))) %>%
  select(a, log_effect_size, reject, conv_or_not)

map_df(levels(dat_heter_a$a), function(x) {

  # Adjust the range of x
  result <- data.frame(log_effect_size = seq(min(dat_heter_a$log_effect_size),
                                             max(dat_heter_a$log_effect_size), 
                                             0.01))

  # Manually fit the model
  conv_mod <- glm(reject ~ log_effect_size, 
                  family = binomial(),
                  data = filter(dat_heter_a, 
                                a == x, 
                                conv_or_not == "Conventional"))

  # Manually fit the model
  visual_mod <- glm(reject ~ log_effect_size, 
                  family = binomial(),
                  data = filter(dat_heter_a, 
                                a == x, 
                                conv_or_not == "Visual"))

  # Get the prediction
  result <- result %>%
    mutate(Conventional = predict(conv_mod, 
                                  newdata = result, 
                                  type = "response"),
           Visual = predict(visual_mod, 
                            newdata = result, 
                            type = "response"),
           a = x) %>%
    pivot_longer(Conventional:Visual, names_to = "conv_or_not")

  result
}) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, value, col = a), se = FALSE, span = 0.03) +
  xlab(expression(log[e] (Effect_size))) +
  ylab("Power") +
  scale_color_manual(values = rcartocolor::carto_pal(3, "Earth")) +
  theme_light() +
  theme(legend.position = "bottom") +
  facet_wrap(~conv_or_not) +
  labs(col = "Heteroskedasticity shape")
```
